Here we will specify the main communication interfaces that can be used to solve the communication and integration of different components.

\begin{enumerate}
    \item eMma and eMci are part of the eMSP that run on separate machines from it. This means that they'll need to communicate using some kind of network protocol. In particular we shall use the internet stack of protocols. Surely up to the transport layer (TCP/UDP) the standard protocols shall be used, meanwhile for the application layer the decision of  weather to use a proprietary protocol or a standard one like \verb|http| shall be let to the architectural designer.
    \item The eMSP needs to communicate with different CPMS. We can't make any assumption on how each different CPMS will provide their services so this part of the eMSP that handles the communication shall be constructed in the most general way. If, during further analysis, this implementation becomes too troublesome and complex, then, an assumption can be made, and is possible to build the system such that it can communicate with only the CPMSs that use the \verb|OCPI| protocol. This second option is preferable for cost-effectiveness.
    \item The CPMS needs to communicate with the software managing the charging points. An open standard protocol has been devised for this purpose and is widely adopted, the OCPP. Our system will be using this protocol to communicate with the charging points.
    \item The CPMS needs to communicate with different DSOs to get information about their prices, sources and other characteristics of the supplied electricity and to conclude a purchase agreement. For this kind of communication there is no open standard protocol, so an ad-hoc interface needs to be build to be able to interface with different DSOs.
\end{enumerate}
\clearpage